Analysis of the 2005--2015 Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2016-08-19 results.tex
revised figure 7

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
	\caption{ $k-M$ relationship for north Iran tectonic seismic regions. The blue circles indicate the connectivity degrees. The red line is the linear regression line fits the data. The numbers on the lines is the slope of the regression lines.}
	\label{fig:km}
\end{figure*}

@@

% \begin{figure*}[t]
% 	\centering
% 	\includegraphics[scale=0.5]{figures/pdf/Figure08.pdf} 
% 	\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence. The numbers on the mean and standard deviation plots are coefficient of variations in percent $(standard \ deviation / mean)$.}
% 	\label{fig:random}
% \end{figure*}

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
	\caption{$k-M$ relationship for north Iran tectonic seismic regions. The blue circles indicate the connectivity degrees. The red line is the linear regression line fits the data. The numbers on the lines is the slope of the regression lines.}
	\label{fig:km}
\end{figure*}

@@

\begin{figure*}%[t]
	\centering
	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-07} 
	\caption{Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence. The numbers on the mean and standard deviation plots are coefficient of variations in percent $(standard \ deviation / mean)$.}
	\label{fig:random}
\end{figure*}
